Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-27 paper/aaaiFormat1.tex
ready to change to lncs format

\def\year{2017}\relax
\documentclass{article}
\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

@@

@@

\begin{table*}[ht]
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
\scalebox{0.76}{
\label{my-label}
\begin{tabular}{|l|L{3cm}|l|l|}
\hline
Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...˙http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 25 \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 20 \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 \\ \hline
\end{tabular}
}
\end{table*}

@@

\textbf{Overall Performances.}
\begin{comment}
Table 1 reports the number of events
detected, the precision and recall, of the three methods respectively.
The results of EDCoW are reproduced from [21]9
. Shown in the
table, our proposed method Twevent yields the best precision of
86.1\% which is significantly larger than the precisions achieved
by EDCoW and Tweventu. Observe that our method Twevent detects
101 events with a recall of 75 realistic events. On the same
dataset, EDCoW detects 21 events in total with 13 realistic events.
Tweventu yields a slighter worse precision than EDCoW (75.3%
vs 76.2\%) but detects the largest number of realistic events. In
terms of DERate, Twevent achieves the lowest rate despite that our
method detects much more events than EDCoW (101 vs 21). On
the other hand, we observe that Tweventu delivers the worst DERate,
more than double of Twevent (41\% vs 16.0\%). That is, the unigrams
about the same event are clustered into two or more events.
Because a tweet segment usually conveys very specific information,
the tweets containing the tweet segment are all about the same
topic (e.g., the event). Two tweet segments about the same event
are therefore have higher chance to be clustered together.
\end{comment}

>>>>

% !Mode:: "TeX:UTF-8"
\def\year{2017}\relax
\documentclass{article}
\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

@@

%TODO, Chinese
\usepackage{CJKutf8}
\inputencoding{utf8}

@@

%\begin{comment}
\begin{table*}[ht]
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
\scalebox{0.76}{
\label{my-label}
\begin{tabular}{|l|L{3cm}|l|l|}
\hline
Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman... http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 25 \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 20 \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 \\ \hline
\end{tabular}
}
\end{table*}
%\end{comment}

@@

\textbf{Overall Performances.}
\begin{CJK*}{UTF8}{gbsn}
    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文
\end{CJK*}

\begin{comment}
Table 1 reports the number of events
detected, the precision and recall, of the three methods respectively.
The results of EDCoW are reproduced from [21]9
. Shown in the
table, our proposed method Twevent yields the best precision of
86.1\% which is significantly larger than the precisions achieved
by EDCoW and Tweventu. Observe that our method Twevent detects
101 events with a recall of 75 realistic events. On the same
dataset, EDCoW detects 21 events in total with 13 realistic events.
Tweventu yields a slighter worse precision than EDCoW (75.3%
vs 76.2\%) but detects the largest number of realistic events. In
terms of DERate, Twevent achieves the lowest rate despite that our
method detects much more events than EDCoW (101 vs 21). On
the other hand, we observe that Tweventu delivers the worst DERate,
more than double of Twevent (41\% vs 16.0\%). That is, the unigrams
about the same event are clustered into two or more events.
Because a tweet segment usually conveys very specific information,
the tweets containing the tweet segment are all about the same
topic (e.g., the event). Two tweet segments about the same event
are therefore have higher chance to be clustered together.
\end{comment}
